Evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-04-28 ms.Rmd
Added some stats methods. Still need details on visual modelling. Removed section numbering

---
title: "Evolution of a conspicuous dynamic visual signal in an introduced chameleon"
author: Whiting et al. 
date: "`r Sys.Date()`"
bibliography: refs.bib
csl: science.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: true
    reference_docx: template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---

@@

Martin J. Whiting $^1,*$, Brenden S. Holland $^2$, J. Scott Keogh$^3$, Daniel W.A.Noble$^3$, Katrina J. Rankin$^4$ and Devi M. Stuart-Fox$^4$

$^1$ Department of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia

@@

Sexual selection is expected to favour more conspicuous dymamic sexual signals in Hawaii under relaxed predation because higher predation should favour cryptic signals whereas greater conspicuousness of sexual signals should be selected in social contexts. In support of this prediction, male display colouration exhibited in social contexts (i.e., male-male contests and courtship) was more conspicuous to a conspecific in Hawaii compared with Kenya (Male-Male Contests: Acromatic contrast ($dl$); $F_{`r anovaConspicDisplayAC$NumDF[2]`,`r anovaConspicDisplayAC$DenDF[2]`}$ = `r anovaConspicDisplayAC[5][2,]`, p = `r p_value(anovaConspicDisplayAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r anovaConspicDisplayCC$NumDF[2]`,`r anovaConspicDisplayCC$DenDF[2]`}$ = `r anovaConspicDisplayCC[5][2,]`, p = `r p_value(anovaConspicDisplayCC[6][2,])`; Courtship displays: Acromatic contrast ($dl$); $F_{`r courship_anovaAC$NumDF[2]`,`r courship_anovaAC$DenDF[2]`}$ = `r courship_anovaAC[5][2,]`, p = `r p_value(courship_anovaAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r courship_anovaCC$NumDF[2]`,`r courship_anovaCC$DenDF[2]`}$ = `r courship_anovaCC[5][2,]`, p = `r p_value(courship_anovaCC[6][2,])`), and this was  true across all body regions measured (See Supplemental Materials, table S1). Kenyan chameleons were significantly more crypic compared to introduced Hawaiian counterparts (Acromatic Contrast between Hawaiian and Kenyan Populations, Male-male contests: $\beta$ = `r coefAIC_display`, 95% CI = `r CI_AC_display[5,1]` to  `r CI_AC_display[5,2]`, df = `r summary(ConspicDisplayAC)$coefficients[3, "df"]`, t =  `r summary(ConspicDisplayAC)$coefficients[3, "t value"]`, p = `r p_value(summary(ConspicDisplayAC)$coefficients[3, "Pr(>|t|)"])`, Courtship: $\beta$ = `r coefAIC_court`, 95% CI = `r CI_AC_court[5,1]` to  `r CI_AC_court[5,2]`, df = `r summary(ConspicCourtshipAC)$coefficients[3, "df"]`, t =  `r summary(ConspicCourtshipAC)$coefficients[3, "t value"]`, p = `r p_value(summary(ConspicCourtshipAC)$coefficients[3, "Pr(>|t|)"])`, see figure 1a & b).

@@

>>>>

---
title: "Evolution of a conspicuous dynamic visual signal in an introduced chameleon"
author: Whiting et al. 
date: "`r Sys.Date()`"
bibliography: refs.bib
csl: science.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: false
    reference_docx: template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---

@@

Martin J. Whiting $^{1,*}$, Brenden S. Holland $^{2}$, J. Scott Keogh$^{3}$, Daniel W.A.Noble$^{3}$, Katrina J. Rankin$^{4}$ and Devi M. Stuart-Fox$^{4}$

$^{1}$ Department of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia

@@

Sexual selection is expected to favour more conspicuous dymamic sexual signals in Hawaii under relaxed predation because higher predation should favour cryptic signals whereas greater conspicuousness of sexual signals should be selected in social contexts. In support of this prediction, male display colouration exhibited in social contexts (i.e., male-male contests and courtship) was more conspicuous to a conspecific in Hawaii compared with Kenya (Male-Male Contests: Acromatic contrast ($dl$); $F_{`r anovaConspicDisplayAC$NumDF[2]`,`r anovaConspicDisplayAC$DenDF[2]`}$ = `r anovaConspicDisplayAC[5][2,]`, p = `r p_value(anovaConspicDisplayAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r anovaConspicDisplayCC$NumDF[2]`,`r anovaConspicDisplayCC$DenDF[2]`}$ = `r anovaConspicDisplayCC[5][2,]`, p = `r p_value(anovaConspicDisplayCC[6][2,])`; Courtship displays: Acromatic contrast ($dl$); $F_{`r courship_anovaAC$NumDF[2]`,`r courship_anovaAC$DenDF[2]`}$ = `r courship_anovaAC[5][2,]`, p = `r p_value(courship_anovaAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r courship_anovaCC$NumDF[2]`,`r courship_anovaCC$DenDF[2]`}$ = `r courship_anovaCC[5][2,]`, p = `r p_value(courship_anovaCC[6][2,])`), and this was  true across all body regions measured (See Supplemental Materials, table S1). Kenyan chameleons from populations where predation is high were significantly more crypic compared to introduced Hawaiian counterparts (Acromatic Contrast between Hawaiian and Kenyan Populations, Male-male contests: $\beta$ = `r coefAIC_display`, 95% CI = `r CI_AC_display[5,1]` to  `r CI_AC_display[5,2]`, df = `r summary(ConspicDisplayAC)$coefficients[3, "df"]`, t =  `r summary(ConspicDisplayAC)$coefficients[3, "t value"]`, p = `r p_value(summary(ConspicDisplayAC)$coefficients[3, "Pr(>|t|)"])`, Courtship: $\beta$ = `r coefAIC_court`, 95% CI = `r CI_AC_court[5,1]` to  `r CI_AC_court[5,2]`, df = `r summary(ConspicCourtshipAC)$coefficients[3, "df"]`, t =  `r summary(ConspicCourtshipAC)$coefficients[3, "t value"]`, p = `r p_value(summary(ConspicCourtshipAC)$coefficients[3, "Pr(>|t|)"])`, see figure 1a & b).

@@

# Materials and Methods

### *Statistical Analysis*

Chromatic and achromatic contrast from visual models, measured in just noticable differences (JNDs), were analysed using linear mixed effects models in R using the `lme4` package (). Across the different contexts (i.e., social contexts, predation and background environments), chromatic and acromatic contrasts were analysed in seperate models as response variables. For analyses involving social context, we included z-transformed snout-vent length (SVL), population of origin, and their interaction as fixed effects. For models involving predatory contexts and visual systems, we included the predator type (i.e, snake or snake), population of origin and their interaction as fixed effects. Finally, to test local adaptation, we used only chameleons from Hawaii and tested the extent to which chromatic and achromatic contrast varied depending on whether Hawaiian signals were obersved on a native Kenyan background or their current introduced habitat background in Hawaii. Model interactions were first tesed using a Type III sum of squares ANOVA with a Saitterwaite degrees of freedom correction, and if found to be non-significant (p > 0.1) we dropped the interaction and fit a main effects model. For all individuals, we measured signals for multiple body regions, each of which were contratsed between multiple background measurements (i.e., 2 random leaves, and 2 random stems). For our main analyses we average estimates across these body regions and background environments given that in many cases body regions showed remarkably similar effects (see Supplementary Results). Deriving multiple contrats for each individual body region and background resulted in a substantial number of comparisons, each of which were not completely indpeendent of each other. To ensure that non-indpendence of data did not impact our inferences we used a Robust Variance Estimator (RVE) on our final model to correct standard errors for within-individual non-independence. In all cases, our results and conclusions were not impacted (see supplmentary code).

# References
